### 2023-04-03 reachable-resilience.tex
up

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets are WSTS with strong upward compatibility (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). 
Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow \post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded state-resilience is decidable for VASS.
Hence state-resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework. Moreover, we may show:

@@

LOREM IPSUM \\

>>>>

The characterization is used to show that Petri nets are $\post^*$-effective.

\begin{proposition}
Let $P = (N,M,W)$ be a Petri net and $s \in M$ a configuration of the Petri net, then one can compute a basis of $\uparrow \post^*(s)$.
\end{proposition}

It is well-known that Petri nets are WSTS with strong upward compatibility (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). 
Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow \post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded state-resilience is decidable for VASS.
Hence state-resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework. Moreover, we may show:

@@

\mathieu{Écrire que c'est globalement symmétrique au cas d'avant - je pense pas nécessairement qu'on arrive à faire beaucoup mieux que de juste dire ça.}
